On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-24 docs/mvfits_paper/mvf.tex
misc updates

Neither method directly accounts for information

>>>>

Neither currently performs cross-validation, given sufficiently dense training data.
And perhaps most notably, neither method directly accounts for information about the noise distribution within the training data.
As such, the methods presented are recommended primarily for datasets where noise is very small or negligible.
Nevertheless, the \gmvr{} toy problem demonstrates \gmvr{}'s ability to handle moderately noisy training data, suggesting current applicability to a large number of problems where polynomial interpolation is insufficient. 
